Merging Datasets Through Deep learning

### 2018-09-04 paper2018/evaluation.tex
spelling
fixed table ref

\section{Experiments}
\label{results}
In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for the adapted loss function from 1-20.  Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.  For all our runs, test accuracy as measured by this metric ranged in the 97-99\% range for the people dataset and 92-94\% companies dataset for all losses except angular loss which was poor throughout.  Table \ref{Evaluation} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.  Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.  For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are means across two runs.

@@

 The results show training on hard negatives produces consistently better results, both for precision and recall.  Hard negative training resulted in recall of 81\% of posiives in the nearest set versus 63\% for semi-hard negatives.  Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.  Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi hard.

>>>>

\section{Experiments}
\label{results}
In building the models, we employed early stopping using the usual metric of accuracy of the validation data, and we performed hyper-parameter tuning using grid search varying margins for the adapted loss function from 1-20.  Accuracy was defined as the percentage of validation triples where positive distances from anchor were less than negative distances from anchor.  For all our runs, test accuracy as measured by this metric ranged in the 97-99\% range for the people dataset and 92-94\% companies dataset for all losses except angular loss which was poor throughout.  Table \ref{precision_recall} shows the results for the people and company datasets, run with a fixed $k$ of 20 neighbors.  Because we compared across different losses, the results are categorized by each loss function for each dataset we tested.  For all the results reported here, we ran multiple runs because of the stochastic nature of neural network models; the results here are means across two runs.

@@

 The results show training on hard negatives produces consistently better results, both for precision and recall.  Hard negative training resulted in recall of 81\% of positives in the nearest set versus 63\% for semi-hard negatives.  Precision@1 is similar, with 81\% for hard negatives versus 61\% for semi-hard.  Overall precision, defined as the fraction of positives closer than any negative is 63\% for hard negatives versus 43\% for semi hard.
